Coherent optical association of a single molecule

### 2020-10-30 paper.tex

Early experiments used weakly-bound excited states as the intermediate state
in the Raman transition to ensure a large Raman Rabi frequency~\cite{Wynar2000,Rom2004}.
However, for a complete picture, the many excited vibrational states in a molecular potential
as well as the excited atomic continuum need to be considered.
The total scattering rate and Raman Rabi rate become a sum of the scattering rates
and Raman Rabi rates over all possible intermediate states.
With these considerations, using a weakly-bound excited state as the intermeidate state
suffers from strong scattering of the nearby excited atomic continuum rendering it incoherent,
resulting in molecule loss \todo{be more clear with "molecule loss". I think you mean:
  resulting in large incoherence and loss to other molecular states.}.
This scattering is proportional to $1/\delta_{thresh}^2$,
where $\delta_{thresh}$ is the detuning from the dissociation threshold,
and thus can be made smaller by using deeply bound vibrational states as the intermediate level.

>>>>

Early experiments used weakly-bound excited states as the intermediate state
in the Raman transition to ensure a large Raman Rabi frequency~\cite{Wynar2000,Rom2004}.
However, for a complete picture, the many excited vibrational states in a molecular potential
as well as the excited atomic continuum need to be considered.
The total scattering rate and Raman Rabi rate become a sum of the scattering rates
and Raman Rabi rates over all possible intermediate states.
With these considerations, using a weakly-bound excited state as the intermeidate state
suffers from strong scattering of the nearby excited atomic continuum rendering it incoherent,
resulting in molecule loss \text{red}{Jon: be more clear with "molecule loss". I think you mean:
  resulting in large incoherence and loss to other molecular states.}.
This scattering is proportional to $1/\delta_{thresh}^2$,
where $\delta_{thresh}$ is the detuning from the dissociation threshold,
and thus can be made smaller by using deeply bound vibrational states as the intermediate level.
